\bf Approximating Likelihood Ratios with Calibrated Discriminative Classifiers

### 2016-03-01 jasa/paper-jasa.tex
Update MLE histogram figure

Let us now consider the composite hypothesis testing setting, by comparing
$H_0: g = 0$ versus the alternative $H_1: g > 0$. That is, we want to evaluate
\begin{equation}
\Lambda({\cal D}; \Theta_0 = \{0\}, \Theta=(0, \frac{1}{2}]) =  \frac{ p({\cal D} | g = 0) }{ \sup_{\theta \in \Theta} p({\cal D} | g=\theta)} \; .
\end{equation}
Following the approach outlined in Section~\ref{sec:generalized-likelihood-ratio},
computing the generalized likelihood ratio statistic requires finding
the maximum likelihood estimator for the denominator, which can be carried out using
approximated likelihood ratios. Reusing the decomposed neural network-based
approximation and minimizing the mean negative log-ratio of some observed data
generated for $g=0.05$,
Figure~\ref{fig:3} shows the empirical distribution of $\hat g$ when repeating the generation and optimization process.
The figure clearly suggests that the proposed inference procedure yields in this case
an unbiased estimator ($\mathbb{E} [\hat g] = 0.0502$, as empirically estimated over $200$ trials).
From there, the generalized likelihood ratio can be approximated as in the simple
hypothesis setting.

>>>>

Let us now consider the composite hypothesis testing setting, by comparing
$H_0: g = 0$ versus the alternative $H_1: g > 0$. That is, we want to evaluate
\begin{equation}
\Lambda({\cal D}; \Theta_0 = \{0\}, \Theta=(0, \frac{1}{2}]) =  \frac{ p({\cal D} | g = 0) }{ \sup_{\theta \in \Theta} p({\cal D} | g=\theta)} \; .
\end{equation}
Following the approach outlined in Section~\ref{sec:generalized-likelihood-ratio},
computing the generalized likelihood ratio statistic requires finding
the maximum likelihood estimator for the denominator, which can be carried out using
approximated likelihood ratios. Reusing the decomposed neural network-based
approximation and minimizing the mean negative log-ratio of some observed data
generated for $g=0.05$,
Figure~\ref{fig:3} shows the empirical distribution of $\hat g$ when repeating the generation and optimization process.
The figure clearly suggests that the proposed inference procedure yields in this case
an unbiased estimator ($\mathbb{E} [\hat g] = 0.04995$, as empirically estimated over $1000$ trials).
From there, the generalized likelihood ratio can be approximated as in the simple
hypothesis setting.
